Is high social class always beneficial for survival? A study of Northern Sweden

### 2017-10-26 article3.Rmd
Correcting author names

---
title: Is high social class always beneficial for survival? A study of Northern Sweden 1801--2013
author: "Sören Edvinsson and Göran Broström"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---

>>>>

---
title: Is high social class always beneficial for survival? A study of Northern Sweden
  1801--2013
author: "Sören Edvinsson and Göran Broström"
date: '`r Sys.Date()`'
output:
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---
